SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
New proof for Th.3 after discussion with Prof.Zhang.

For each of these, define $States: <OT> \rightarrow <State>$ which is the function computing the set of states in a set of OTs. Between two transitions sets of the
algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function renaming fresh variables.

@@

\begin{theorem}[Correctness with assignments]
  \label{Th:CorrectnessWithAssignments}
In the general case, the smart algorithm computes 
the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transition labels.
\end{theorem}

\TODO{Formalize the proof}

@@

  \medskip
  \noteInEM{I keep below the original proof draft from Xudong, though
    think it does not apply any more}
\begin{proof}
In Theorem 2, we have already proved the result set of global states of two algorithm are the same without the assignments.

If there exists assignments in the open transitions.

In Algorithm 3, $\forall\ostate{\tilde{t}}\notin State(L_{Smart})$, if there is a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, we need to check $\textit{Pred}\and\bigwedge\textit{Post}_i$ where $\textit{Post}_i \notin \{\textit{Post}_t\}$.

In Algorithm 1, the same state $\ostate{\tilde{t}}\notin State(L1)$, also has a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, what need to check is $\textit{Pred}\and\bigwedge\textit{Post}_i$.
As $b_1\and b_2\rightarrow b_1$, if $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$ exists in the result of Algorithm 3, it is also contained in the original result.

After the final reachability computation, $\{\textit{Post}_t\}$ is removed from $\{\textit{Post}_i\}$ then the assertions to check become the same, then the transitions of the result are also the same. So the result open automaton of Algorithm 3 is exactly the same as that of  Algorithm 1.
\end{proof}

>>>>

For each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of states in a set of OTs. Between two transitions sets of the
algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function renaming fresh variables.

@@

\begin{theorem}[Correctness with assignments]
  \label{Th:CorrectnessWithAssignments}
In the general case, if a pNet contains some assignments to state variables, the smart algorithm computes 
the same open automaton as that of Algorithm 1 up to a renaming of variables in the transition labels.
\end{theorem}

\TODO{Formalize the proof}
\begin{proof}
In Theorem 2, we have already proved the result automaton $OA_1$ and $OA_2$ of two algorithm are the same without the assignments.

Define the function $States$ as before, and  $Assignments : \langle OT\rangle\times\langle State\rangle\rightarrow\langle Assign\rangle$ the function
computing the set of assignments of a global state from a given set of OTs.

The structure implicitely computed by the algorithm (comprised in
the structure of an Open Automaton) is a triple $ Aut= \langle OTs, States, Assigns\rangle$.

Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{reach}, States(L2_{reach}))$. The computed triples are 
\[Aut_1 = \langle L1_{reach}, States(L1_{reach}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{reach}, States(L2_{reach}), Assignments(L2_{reach}, States(L2_{reach}))\rangle\]

Based on the notation of the triple, define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
\begin{align*}
Refine(Aut) &=\langle OT', States(OT'), Assignments(OT', States(OT'))\rangle \\
&=Aut'
\end{align*}
where $OT' = OT - OT_{unsat}$, $OT_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.

Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n|\le |Aut^{n-1}|$.
Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.

Let the fixed point of $OA_1$ to be $Aut''_1$ and the fixed point of $OA_2$ to be $Aut''_2$.

For the transitions set in $Aut''_1$ and $Aut''_2$, $L1_{reach}''$ and $L2''_{reach}$, we need to check their equivalence.
At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case.
\begin{align*}
&\quad Pred\and \bigwedge_i Assignments_i(L1, States(L1) \text{ is false}\\
&\quad\rightarrow Pred \and \bigwedge_j Assignments_j(L2_{reach}, States(L2_{reach})\text{ is false}\\
&\Rightarrow \forall t\in L1_{unsat} \rightarrow t\in L2_{unsat}\\
&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
\end{align*}
However, its reverse direction is not fulfilled. Recall that $L1_{reach}=L2_{reach}$, these relation can imply that,
\begin{align*}
Assignments(L1, &States(L1)\supseteq Assignments(L2_{reach}, States(L2_{reach})\\
&\supseteq Assignments(L1_{reach}-L1_{unsat}, States(L1_{reach}-L1_{unsat}))\\
&\supseteq Assignments(L2_{reach}-L2_{unsat}, States(L2_{reach}-L2_{unsat}))
\end{align*}
So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases.
\begin{align*}
&\forall t\in L1'_{unsat} \rightarrow t\in L2'_{unsat}\\
\text{ or }&\forall t\in L1'_{unsat} \rightarrow t\notin L2'_{reach}.
\end{align*}
By induction, after removing all the transitions not in the $L2''_{reach}$, we can get that $L1''_{reach}=L2''_{reach}$, subsequently, $States(L1''_{reach})=States(L2''_{reach})$,
$Assignments\\(L1''_{reach},States''_{L1_{reach}})=Assignments(L2''_{reach},States''_{L2_{reach}})$.
\end{proof}

@@

  \medskip
  \noteInEM{I keep below the original proof draft from Xudong, though
    think it does not apply any more}
